New lower bounds for Schur and weak Schur numbers

### 2021-06-07 article/article.tex
Deuxième série de corrections - partie WS (dans le bon dossier)
environnements figure

\usepackage[english]{babel}
\usepackage[hyphens]{url}
\usepackage{hyperref}
\usepackage[utf8]{inputenc}
\usepackage{siunitx}

@@

\par
The fourth section gives new insight on the method that was formerly used to achieve new lower bounds for weak 
Schur numbers. The assumption behind it might have removed the optimal partitions from the search space and thus 
lowered the highest value that can be reached within it. However, the methods used to explore this search space 
are efficient as the optimum was found. Thereby Monte-Carlo algorithms may prove to be very useful if used in a 
search space with more potential. Finding a weakly sum-free partition which is better than previous lower bounds 
and which is not as regular as those obtained with templates would be extremely interesting (even if it does not 
improve current lower bounds) since it could suggest a new search space which could then be explored with the 
above mentioned methods.

>>>>

\usepackage[english]{babel}
\usepackage[hyphens]{url}
\usepackage{hyperref}
\usepackage[utf8]{inputenc}
\usepackage{siunitx}
\usepackage{float}

@@

### 2021-06-07 article/schur.tex
environnements figure

\renewcommand{\arraystretch}{1.7}

\begin{center}
\setlength{\tabcolsep}{1.5ex}

@@

\setlength{\tabcolsep}{6pt}
\end{center}

In the general construction with S-templates, the special color no longer necessarily contains consecutive 
numbers. However, the special color is still replaced by the colors of the sum-free partition according to the 
line number and the other colors are still vertically extended.

\begin{center}
\setlength{\tabcolsep}{1.5ex}

\textbf{S-template construction}
\vspace{1.7ex}

@@

\setlength{\tabcolsep}{6pt}
\end{center}

@@

\begin{table}[H]
\caption{New lower bounds for \( n \in [\![8,15]\!] \)}
\label{LowerBoundsWS}
\[
\begin{array}{c}
	\resetarraystretch
	\begin{NiceArray}{cwc{8ex}wc{10ex}wc{10ex}wc{11ex}}[hvlines]
	\CodeBefore
		\cellcolor{yellow}{2-2}
		\cellcolor{yellow}{3-3}
		\cellcolor{yellow}{4-4}
		\cellcolor{yellow}{4-5}
	\Body
		n & 8 & 9 & 10 & 11 \\
		33 \, S(n-3) + 6 & 5\,286 & 17\,694 & 55\,446 & 174\,444 \\
		111 \, S(n-4) + 43 & 4927 & 17\,803 & 59\,539 & 186\,523 \\
		380 \, S(n-5) + 148 & 5\,088 & 16\,868 & 60\,948 & 203\,828 \\
	\end{NiceArray}
	\\ \\
	\resetarraystretch
	\begin{NiceArray}{cwc{8ex}wc{10ex}wc{10ex}wc{11ex}}[hvlines]
	\CodeBefore
		\cellcolor{yellow}{2-3}
		\cellcolor{yellow}{4-2}
		\cellcolor{yellow}{4-4}
		\cellcolor{yellow}{4-5}
	\Body
		n & 12 & 13 & 14 & 15 \\
		33 \, S(n-3) + 6 & 587\,505 & 2\,011\,290 & 6\,726\,330 & 21\,072\,090 \\
		111 \, S(n-4) + 43 & 586\,789 & 1\,976\,176 & 6\,765\,271 & 22\,624\,951 \\
		380 \, S(n-5) + 148 & 638\,548 & 2\,008\,828 & 6\,765\,288 & 23\,160\,388 \\
	\end{NiceArray}
\end{array}
\]
\end{table}
\resetarraystretch

>>>>

\renewcommand{\arraystretch}{1.7}
\begin{figure}[H]
\begin{center}
\setlength{\tabcolsep}{1.5ex}

@@

\setlength{\tabcolsep}{6pt}
\caption{Visualisation of an Abbott and Hanson construction}
\end{center}
\label{figure:1}
\end{figure}
In the general construction with S-templates, the special color no longer necessarily contains consecutive 
numbers. However, the special color is still replaced by the colors of the sum-free partition according to the 
line number and the other colors are still vertically extended.

\begin{figure}[H]
\begin{center}
\textbf{S-template construction}
\setlength{\tabcolsep}{1.5ex}

\vspace{1.7ex}

@@

\setlength{\tabcolsep}{6pt}
\caption{Visualisation of a template-based construction}
\label{figure:2}

\end{center}
\end{figure}

@@

\begin{table}[H]

\label{LowerBoundsWS}
\[
\begin{array}{c}
	\resetarraystretch
	\begin{NiceArray}{cwc{8ex}wc{10ex}wc{10ex}wc{11ex}}[hvlines]
	\CodeBefore
		\cellcolor{yellow}{2-2}
		\cellcolor{yellow}{3-3}
		\cellcolor{yellow}{4-4}
		\cellcolor{yellow}{4-5}
	\Body
		n & 8 & 9 & 10 & 11 \\
		33 \, S(n-3) + 6 & 5\,286 & 17\,694 & 55\,446 & 174\,444 \\
		111 \, S(n-4) + 43 & 4927 & 17\,803 & 59\,539 & 186\,523 \\
		380 \, S(n-5) + 148 & 5\,088 & 16\,868 & 60\,948 & 203\,828 \\
	\end{NiceArray}
	\\ \\
	\resetarraystretch
	\begin{NiceArray}{cwc{8ex}wc{10ex}wc{10ex}wc{11ex}}[hvlines]
	\CodeBefore
		\cellcolor{yellow}{2-3}
		\cellcolor{yellow}{4-2}
		\cellcolor{yellow}{4-4}
		\cellcolor{yellow}{4-5}
	\Body
		n & 12 & 13 & 14 & 15 \\
		33 \, S(n-3) + 6 & 587\,505 & 2\,011\,290 & 6\,726\,330 & 21\,072\,090 \\
		111 \, S(n-4) + 43 & 586\,789 & 1\,976\,176 & 6\,765\,271 & 22\,624\,951 \\
		380 \, S(n-5) + 148 & 638\,548 & 2\,008\,828 & 6\,765\,288 & 23\,160\,388 \\
	\end{NiceArray}
\end{array}
\]
\caption{New lower bounds for \( n \in [\![8,15]\!] \)}
\end{table}
\resetarraystretch
